The Radio Sky at Meter Wavelengths: $m$-Mode Analysis Imaging\\ with the Owens Valley Long Wavelength Array

### 2017-10-24 paper.tex
add chalmers affiliation for stephen and acknowledgements from gregg

@@

% alphabetical by last name
\author{Benjamin~R.~Barsdell} \harvard \nvidia
\author{Stephen~A.~Bourke}    \astrocaltech
\author{M.~A.~Clark}          \nvidia
\author{Steven~W.~Ellingson}  \vt
\author{Jayce~Dowell}         \unm
\author{Hugh~Garsden}         \harvard
\author{Lincoln~J.~Greenhill} \harvard
\author{Jonathon~Kocz}        \astrocaltech
\author{T.~Joseph~W.~Lazio}   \jpl
\author{Danny~C.~Price}       \harvard \berkeley \swinburne
\author{Frank~K.~Schinzel}    \nrao \unm
\author{Gregory~B.~Taylor}    \unm
\author{Yuankun~Wang}         \astrocaltech
\author{David~P.~Woody}       \ovro

@@

>>>>

\newcommand{\chalmers}{
    \affiliation{
        Department of Space, Earth and Environment,
        Chalmers University of Technology,
        Onsala Space Observatory,
        43992 Onsala,
        Sweden
    }
}

@@

% alphabetical by last name
\author{Benjamin~R.~Barsdell} \harvard \nvidia
\author{Stephen~A.~Bourke}    \astrocaltech \chalmers
\author{M.~A.~Clark}          \nvidia
\author{Steven~W.~Ellingson}  \vt
\author{Jayce~Dowell}         \unm
\author{Hugh~Garsden}         \harvard
\author{Lincoln~J.~Greenhill} \harvard
\author{Jonathon~Kocz}        \astrocaltech
\author{T.~Joseph~W.~Lazio}   \jpl
\author{Danny~C.~Price}       \harvard \berkeley \swinburne
\author{Frank~K.~Schinzel}    \nrao \unm
\author{Gregory~B.~Taylor}    \unm
\author{Yuankun~Wang}         \astrocaltech
\author{David~P.~Woody}       \ovro

@@

This material is based in part upon work supported by the National Science Foundation under Grant
AST-1654815 and AST-1212226. The OVRO-LWA project was initiated through the kind donation of Deborah
Castleman and Harold Rosen.
